\bf Model Visualization Techniques for a Social Network Model

### 2017-06-02 paper.Rnw
add refs to adjmat and nodelink diags

\section{Introduction} 
% \st{
% \begin{itemize}
% %\item What? - model visualization and SAOMs. briefly dsecribe what these things are
% %\item Why? - bring light to the RSiena blackbox. Need ways to visualize network models, collections of networks. 
% \item How?
% \end{itemize}
% %also talk about other dynamic network models briefly to put SAOMs in context.
% }
\hh{XXX - talk a bit about social networks first, why we want to model them, and that usually the models are not dynamic.}

@@

There are two primary methods used to visualize networks: node-link diagrams and matrix visualization. XX INSERT REFS XX
%\hh{As a toy example, let us assume that we have five nodes, $\{1,2,3,4,5\}$, connected by some edges: XXX list edges as $1 \mapto 2, 2 \mapto 4, ...$ }
We will use the toy data set shown below to demonstrate these two methods.

\hh{XXX describe the dataset in words, but not with the code. }
<<toyex>>=
set.seed(81393)
nodes <- data.frame(id = 1:5, group = sample(LETTERS[1:2], size = 5, replace = T), stringsAsFactors = F)
g <- igraph::as_data_frame(igraph::random.graph.game(n = 5, p = .4))
toynet <- list(nodes = nodes, edges = rbind(g, c(5,4)))
toynet
@

>>>>

\section{Introduction} 
% \st{
% \begin{itemize}
% %\item What? - model visualization and SAOMs. briefly dsecribe what these things are
% %\item Why? - bring light to the RSiena blackbox. Need ways to visualize network models, collections of networks. 
% \item How?
% \end{itemize}
% %also talk about other dynamic network models briefly to put SAOMs in context.
% }
%\hh{XXX - talk a bit about social networks first, why we want to model them, and that usually the models are not dynamic.}

@@

There are two primary methods used to visualize networks: node-link diagrams and matrix visualization \citep{knuth2000, adjmatpro}. As a toy example, let us assume that we have five nodes, $\{1,2,3,4,5\}$, connected by five edges:  $\{2 \mapto 4, 3 \mapto 4, 1 \mapto 5, 3 \mapto 5, 5 \mapto 4\}$ We use this toy data set to demonstrate the two visualization methods in Figure~\ref{fig:toyplots}.

<<toyex, echo = FALSE>>=
set.seed(81393)
nodes <- data.frame(id = 1:5, group = sample(LETTERS[1:2], size = 5, replace = T), stringsAsFactors = F)
g <- igraph::as_data_frame(igraph::random.graph.game(n = 5, p = .4))
toynet <- list(nodes = nodes, edges = rbind(g, c(5,4)))
@
